---
title: "Code for Calculations Performed in 'Economic Motivators and Traits'"
author: "Moses Glickman"
date: "4/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading in Datasets
```{r, echo=T}
library(tidyverse)
library(haven)
ess18 <- read_dta("ESS_2018.dta")
ees19 <- read_dta("ees_2019.dta")
evs_joint <- read_dta("evsjoint.dta")
```
###Time fixed effects
```{r, echo=T}
ess18$date_fe <- as.factor(ess18$inwyye)
ees19$date_fe <- as.factor(2019)
evs_joint$date_fe <- as.factor(evs_joint$year)
```


##Addition of national dummies
```{r, echo=T}
#National dummies
ees19$natdummy <- substr(ees19$region_NUTS1,1,2)
ees19$natdummy[ees19$natdummy=="96"] <- "FR"
evs_joint$natdummy <- evs_joint$cntry_AN
ess18$natdummy <- ess18$cntry
```

###Adding in dataset dummies
```{r, echo=T}
#1=WVS,2=EVS,3=EEs,4=ESS
evs_joint$datadummy = ifelse(evs_joint$studytit=="WVS7",1,2)
ees19$datadummy = 3
ess18$datadummy = 4
```

###Dataset Party Integration: EES
```{r,echo=T}
ees_parties <- read.csv("ees_parties.csv")
ees_parties$Q9 <- ees_parties$Value..Q9. 
ees_parties[is.na(ees_parties)| is.null(ees_parties)]=0
eeslab <- merge(ees19, ees_parties, by="Q9")
```

```{r, echo=T}
esstoy <- ess18
esstoy_a <- esstoy[,c(26:31,32:45,48:57)]
esstoy_a[is.na(esstoy_a)]<-0
esstoy[,c(26:31,32:45,48:57)] <- esstoy_a
esstoy$party <- apply(esstoy[,c(26:31,32:45,48:57)],1,max,na.rm=T)
ess_parties <- read.csv("ess_parties.csv")
ess_parties[is.na(ess_parties) | is.null(ess_parties)]=0
esslab <- merge(esstoy, ess_parties, by.x=c("cntry","party"),by.y=c("Abbreviation","Value"))
```

```{r, echo=T}
evs_parties <- read.csv("evs_parties.csv")
evs_parties[is.na(evs_parties) | is.null(evs_parties)]<-0
evslab <- merge(evs_joint, evs_parties, by.x="E181_EVS5", by.y="Value")
evs_joint_greece <- filter(evs_joint, cntry_AN == "GR")
evslabgreece <- merge(evs_joint_greece, evs_parties, by.x="E179_WVS7", by.y="Value")
evslab <- rbind.data.frame(evslab, evslabgreece)
```



###Manifesto references
```{r, echo=T}
#Middle class prof: per704
#Labor unions: per701
#Welfare state exp: per504
#Immigration: per602_2
#Environmentalism: per501
#EU/European Community: per108
```


### Drop pre-election variables from selected surveys
```{r, echo=T}
#ESS
#inwdds, inwmms, inwyys
esslabdrop <- filter(esslab,
  (cntry != "PT" | (inwyys > 2019) | 
     (inwyys == 2019 & inwmms > 10) | 
     (inwyys==2019 & inwmms == 10 & inwdds > 6)) &
  (cntry != "SE" | (inwyys > 2018) | 
     (inwyys == 2018 & inwmms > 9) | 
     (inwyys==2018 & inwmms == 9 & inwdds > 9)) &
  (cntry != "ES" | (inwyys > 2019) | 
     (inwyys == 2019 & inwmms > 11) | 
     (inwyys==2019 & inwmms == 11 & inwdds > 10)))
#EES
eeslabdrop <- filter(eeslab,
    (Nation == "Greece"))
eeslabdrop <- eeslabdrop[order(eeslabdrop$meta_start_date),][618:700,]
eeslabdrop <- rbind.data.frame(eeslabdrop, filter(eeslab, Nation != "Greece"))
#EVS
evslabdrop <- filter(evslab, 
        (cntry_AN != "CZ" | ivdate > 20171021) & 
        (cntry_AN != "HU" | ivdate > 20180408) &
        (cntry_AN != "IS" | ivdate > 20171028))
```


###Integration of national factors
```{r, echo=T}
natfac <- read.csv("national_factors.csv")
natfac_evs <- filter(natfac, EVS==1)
natfac_ees <- filter(natfac, EES==1)
natfac_ess <- filter(natfac, ESS==1)
evsnat <- merge(evslabdrop, natfac_evs, by.x="cntry_AN", by.y="NatCode")
essnat <- merge(esslabdrop, natfac_ess, by.x="cntry", by.y="NatCode")
eesnat <- merge(eeslabdrop, natfac_ees, by.x="Nation", by.y="Nation")
```

##Comments for dataset var representation

```{r, echo=T}
###Union data
eesnat$Union <- as.numeric(eesnat$D1 %in% c(1,3))
essnat$Union <- as.numeric(essnat$mbtru == 1)
evsnat$Union <- as.numeric(evsnat$A067==1)
###ees19$D1 = 1 or =3: yes, trade union member
###ess18$mbtru = 1: yes, trade union member
###evs_joint$A067 = 1: yes, trade union member
```

```{r, echo=T}
###Gender
#0=male, 1=female, 2=oth
evsnat$Gender <- as.factor(pmin(2, abs(evsnat$X001 - 1)))
essnat$Gender <- as.factor(essnat$gndr - 1)
eesnat$Gender <- as.factor(eesnat$D3 - 1)
###evs_joint$X001 = 2, female; 1, male, -5, other
###ess18$gndr = 2, female; 1, male
###ees19$D3 = 2, female; 1, male; 3, other
```

```{r, echo=T}
###Age
evsnat$Age <- as.numeric(evsnat$X003)
evsnat$Age[evsnat$Age < 16] <- NA
essnat$Age <- as.numeric(essnat$agea)
eesnat$Age <- 2019-eesnat$D4_1
###(2019-ees19$D4_1) = age
###ess19$agea = age
###evs_joint$X003 = age, missing if <16; 82 = 82+
```

```{r, echo=T}
###Income
##EVS
evsnat$Income <- as.numeric(pmax(evsnat$X047_WVS7, evsnat$X047E_EVS5))
evsnat$Income[evsnat$Income < 1] <- NA
##ESS
essnat$Income <- essnat$hinctnta
##EES
eesnat$Income <- as.numeric(eesnat$D11)
eesnat$Income[eesnat$Income > 7] <- NA
eesmean <- mean(eesnat$Income, na.rm=T)
decmean <- mean(c(essnat$Income, evsnat$Income), na.rm=T)
eesnat$Income <- eesnat$Income*decmean/eesmean
rm(eesmean, decmean)
```


```{r, echo=T}
###Marital status
eesnat$MarStat <- eesnat$D5 %in% c(1:4)
essnat$MarStat <- essnat$maritalb==1
evsnat$MarStat <- evsnat$X007
evsnat$MarStat[evsnat$MarStat < 1] <- NA
evsnat$MarStat <- evsnat$MarStat == 1
```

```{r, echo=T}
##Current/former public worker
essnat$PubWork <- essnat$tporgwk %in% c(1:3)
eesnat$PubWork <- eesnat$D6a
eesnat$PubWork[eesnat$PubWork > 95] <- NA
eesnat$PubWork <- eesnat$PubWork==2 | eesnat$PubWork==4
evsnat$PubWork <- evsnat$X052
evsnat$PubWork[evsnat$PubWork<1] <- NA
evsnat$PubWork <- evsnat$PubWork==1
##Public worker (or fpw)
##public worker if ess18$tporgwk = 1,2,3
##public worker if ess19$D6a = 2,4
##public worker if evs_joint$X052 = 1
```

```{r, echo=T}
###EU/Europarl trust
evsnat$EuroTrust <- evsnat$E069_18
evsnat$EuroTrust[evsnat$EuroTrust < 1] <- NA
evsnat$EuroTrust <- 5-evsnat$EuroTrust
eesnat$EuroTrust <- eesnat$Q18_2
eesnat$EuroTrust[eesnat$EuroTrust > 6] <- NA
eesnat$EuroTrust <- 6-eesnat$EuroTrust
essnat$EuroTrust <- essnat$trstep
essmean <- mean(essnat$EuroTrust, na.rm=T)
evsmean <- mean(evsnat$EuroTrust, na.rm=T)
eesmean <- mean(eesnat$EuroTrust, na.rm=T)
evsnat$EuroTrust <- evsnat$EuroTrust * 5 / evsmean
essnat$EuroTrust <- essnat$EuroTrust * 5 / essmean
eesnat$EuroTrust <- eesnat$EuroTrust * 5 / eesmean
rm(essmean, evsmean, eesmean)
###for non-EU countries av is limited in EVS
###but evs_joint$E069_18 = 4 means no trust in EU
##ess18$trstep 0-10, incr trust, for Europarl
##ees19$Q18_2 1-5, with decr. trust, for Europarl
```


```{r, echo=T}
###Urb/rural
eesnat$Urban <- eesnat$D8 != 1
essnat$Urban <- essnat$domicil == 1 | essnat$domicil==2 | essnat$domicil==3
evsnat$Urban <- evsnat$size_5c %in% c(3:5)
#ees19$D8 : 1-rural; 2-small/med town; 3-large town
#ess18$domicil: 1- big city; 2-suburbs; 3-small city; 4-country village; 5-farm/jome in cside
#evs_joint$size_5c: 1-<5k, 2<20k, 3<100k, 4<500k, 5 500k+
```

```{r, echo=T}
##Education
##EVS
evsnat$Edu <- evsnat$X025A_01
evsnat$Edu <- (evsnat$Edu %in% c(0:1)) +
  2*(evsnat$Edu == 2) + 3*(evsnat$Edu==3) +
  4*(evsnat$Edu %in% c(4:5)) +
  5*(evsnat$Edu == 6) +
  6*(evsnat$Edu>6)
evsnat$Edu[evsnat$Edu == 0] <- NA
evsnat$Edu <- as.factor(evsnat$Edu)
##ESS
essnat$Edu <- essnat$eisced
essnat$Edu[essnat$Edu>9]<-NA
essnat$Edu <- (essnat$Edu==1) + 2*(essnat$Edu==2) +
  3*(essnat$Edu %in% c(3,4)) + 4*(essnat$Edu==5) +
  5*(essnat$Edu==6) + 6*(essnat$Edu>6)
essnat$Edu <- as.factor(essnat$Edu)
##EES
eesnat$Edu <- eesnat$D2
eesnat$Edu[eesnat$Edu==97] <- eesnat$Age[eesnat$Edu==97]
eesnat$Edu[eesnat$Edu==99] <- NA
eesnat$Edu <- 1 + (eesnat$Edu>=13) + (eesnat$Edu>=17) +
  (eesnat$Edu>=20) + (eesnat$Edu>=22) +
  (eesnat$Edu>=25)
eesnat$Edu <- as.factor(eesnat$Edu)
#Category ESS; EVS; EES
#Primary 1; 0-1. <13
#Lower Secondary 2; 2, <17
#HS 3,4; 3, <20
#Assoc 5; 4-5, <=21
#Bach 6; 6; <=23
#Grad 7; 7-8 >24
#primary school ends at <13
#secondary at <17
#HS < 
#Bachelor <= 23
#Grad >23
##ess saved in Educode
##ees19$D2: age left edu, 97=still studying
##evs_joint$X025A_01: <0 missing, saved
```

```{r, echo=T}
##Empl status
evsnat$Empl <- evsnat$X028
evsnat$Empl[evsnat$Empl<1] <- NA
evsnat$Empl <- as.numeric((evsnat$Empl==1) + (evsnat$Empl==3))
essnat$Empl <- as.numeric(essnat$mnactic==1)
eesnat$Empl <- as.numeric(eesnat$D6 %in% c(1,2))
#evs_joint$X028 1=fulltime,2=ptime,3=selfemp,7=unemp
#ees19$D6 2=emp,1=selfemp,6=unemp
#ess18$mnactic 1=paid work, 3=unemp looking, 4=unemp nlooking
```


### Dataset trimming
```{r, echo=T}
ess_formerge <- essnat[,c(574:576, 578, 580:619)]
ees_formerge <- eesnat[,c(131:133, 135, 138:143, 1, 145:177)]
evs_formerge <- evsnat[,232:277]
evs_formerge <- evs_formerge[,-c(4,6)]
colnames(evs_formerge)[11] <- "Nation"
colnames(ess_formerge)[11] <- "Nation"
merged_db <- rbind.data.frame(ess_formerge, ees_formerge, evs_formerge)
merged_db$FarR[merged_db$FarR != 1] <- 0
merged_db$FarR <- as.numeric(merged_db$FarR)
```

### Portugal income imputation
```{r, echo=T}
portugal_db <- filter(merged_db, Nation=="Portugal", Election=="10/4/2015")
model <- lm(Income~Empl+Gender+Edu+Urban+PubWork+Age+EuroTrust,data=portugal_db)
library(car)
pdb2 <- filter(merged_db, Nation=="Portugal", Election!="10/4/2015")
pdb2$Income <- Predict(model, pdb2, se=TRUE)$fit
merged_db <- rbind.data.frame(filter(merged_db, Nation != "Portugal" | Election == "10/4/2015"),pdb2)
```

### Incorp of population for weighting
```{r, echo=T}
##https://data.worldbank.org/indicator/SP.POP.TOTL
##psize function is (population*avgleft/#resp) / mean(population*avgleft/#resp) 
##popsize func is (population/#resp) / mean(population/#resp) 
##equal weighting is #resp/mean(#resp)
popdb <- read.csv("population_db.csv")
merged_db <- merge(merged_db, popdb, by="Nation")
nattab <- as.data.frame(table(merged_db$Nation))
colnames(nattab) <- c("Nation", "Frequency")
merged_db <- merge(merged_db, nattab, by="Nation")
merged_db$eqweight <- 1 / merged_db$Frequency
merged_db$eqweight <- merged_db$eqweight / mean(merged_db$eqweight)
ratepop <- mean(merged_db$Population/merged_db$Frequency)
merged_db$popweight <- merged_db$Population / (merged_db$Frequency * ratepop)
```

###Generation of education regression (internal use, not necessary to run)
```{r, echo=T}
#library(dplyr)
#library(olsrr)
#mdb_nees <- filter(merged_db, datadummy !=3)
#mdb_nees$Edu <- as.numeric(mdb_nees$Edu)
#model <- lm(Edu~Income+Empl+Gender+Urban+EuroTrust+PubWork+Age+MarStat+Union+Nation+Left+CenR+CLib.G+FarR+NI+Comm, data=mdb_nees)
#ols_step_both_p(model)
#Income, Empl, PubWork, Age, Union, Nation, Urban, EuroTrust, CLib.G
#mod2 <- lm(Edu~Income+Empl+PubWork+Age+Union+Urban+EuroTrust+CLib.G, data=mdb_nees)
#library(car)
#ees_model <- ees_formerge
#ees_model$Edu2 <- as.numeric(ees_model$Edu)
#ees_model$Edu <- Predict(mod2, ees_model, se=TRUE)$fit
#mean(ees_model$Edu,na.rm=T)
#mean(ees_model$Edu2,na.rm=T)
#summary(lm(Left~Age+Gender+Income+Empl+Edu+Urban, data=mdb_nees))
#summary(lm(Left~Age+Gender+Income+Empl+Edu+Urban, data=ees_model))
#summary(lm(Left~Age+Gender+Income+Empl+Edu2+Urban, data=ees_model))
```


### Gallagher testing (internal use, not necessary to run)

```{R, echo=T}
#summary(glm(Left~Age+Gender+Income+I(Union*WelfPos)+Union+Consol, data=merged_db))
#summary(glm(Left~Age+Gender+Income+I(Union*WelfPos)+Union+Gallagher_LSq, data=merged_db))
#summary(glm(Left~Age+Gender+Income+I(Union*WelfPos)+Union+Gallagher_Prev_LSq, data=merged_db))
#summary(glm(Left~Age+Gender+Income+I(Union*WelfPos)+Union+Gallagher_ENEP, data=merged_db))
#summary(glm(Left~Age+Gender+Income+I(Union*WelfPos)+Union+Consol+Gallagher_LSq+Gallagher_Prev_ENEP+Gallagher_ENEP+Gallagher_Prev_LSq, data=merged_db))

##Current ENEP more useful than former; current LSq less useful than former
```

### Creating by-nation table of party categories above inclusion threshold
```{r, echo=T}
merged_db$PSec <- as.factor(merged_db$Left + 2*merged_db$CenR + 3*merged_db$CLib.G + 4*merged_db$FarR + 5*merged_db$NI + 6*merged_db$Comm)
levels(merged_db$PSec) <- c("Left", "CenR", "CLib.G", "FarR", "NI", "Comm")
mdb_junk <- merged_db
mdb_junk$UnionYes = ifelse(mdb_junk$Union==1, mdb_junk$PSec=="Left", NA)
mdb_junk$PubYes = ifelse(mdb_junk$PubWork==1, mdb_junk$PSec=="Left", NA)
mdb_junk$UrbYes = ifelse(mdb_junk$Urban==1, mdb_junk$PSec=="Left", NA)
mdb_junk$EuroYes = ifelse(mdb_junk$PSec=="Left", mdb_junk$EuroTrust, NA)
mdb_junk$IncomeAvg = ifelse(mdb_junk$PSec=="Left", mdb_junk$Income, NA)
mdb_junk <- mdb_junk %>% group_by(Nation, Election) %>% summarise(avgcomm=mean(Comm), avgni=mean(NI), avgleft = mean(Left), avgcenr=mean(CenR), avgclibg=mean(CLib.G), avgfarr=mean(FarR), avgunion=mean(Union, na.rm=T),avgpubwork=mean(PubWork, na.rm=T), Population=mean(Population),popweight=mean(popweight),eqweight=mean(eqweight),
                                                                  unionp = mean(UnionYes, na.rm=T), pubp = mean(PubYes, na.rm=T), urbp = mean(UrbYes, na.rm=T), IncomeAvg = mean(IncomeAvg, na.rm=T), euromean = mean(EuroTrust, na.rm=T), europ = mean(EuroYes, na.rm=T))
mdb_junk$Comm <- as.numeric(mdb_junk$avgcomm > 0.05)
mdb_junk$NI <- as.numeric(mdb_junk$avgni > 0.05)
mdb_junk$Left <- as.numeric(mdb_junk$avgleft > 0.05)
mdb_junk$CenR <- as.numeric(mdb_junk$avgcenr > 0.05)
mdb_junk$FarR <- as.numeric(mdb_junk$avgfarr > 0.05)
mdb_junk$CLib.G <- as.numeric(mdb_junk$avgclibg > 0.05)
mdb_junk$union_prem <- mdb_junk$unionp - mdb_junk$avgleft
mdb_junk$union_prop_prem <- mdb_junk$unionp / mdb_junk$avgleft
mdb_junk$pub_prem <- mdb_junk$pubp - mdb_junk$avgleft
mdb_junk$pub_prop_prem <- mdb_junk$pubp / mdb_junk$avgleft
mdb_junk$urb_prem <- mdb_junk$urbp - mdb_junk$avgleft
mdb_junk$urb_prop_prem <- mdb_junk$urbp / mdb_junk$avgleft
mdb_junk$euro_prem <- mdb_junk$europ - mdb_junk$euromean
mdb_junk$euro_prop_prem <- mdb_junk$europ / mdb_junk$avgleft

```

###Generating function to filter party categories
```{r, echo=T}
library(dfidx)
library(mlogit)
library(nnet)
library(dplyr)
trimdown <- function(cname, elec){
  indices = colnames(mdb_junk)[which(filter(mdb_junk, Nation==cname & Election==elec)==1)]
  mdb_junk_1 <- filter(merged_db, Nation==cname & Election==elec & PSec %in% indices)
  mdb_junk_1$PSec <- as.factor(as.character(mdb_junk_1$PSec))
  test <- multinom(PSec~Union+Gender+PubWork+Edu+Empl+Urban+Income+EuroTrust+Age+MarStat, data=mdb_junk_1)
  z <- summary(test)$coefficients/summary(test)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
  p <- (1 - pnorm(abs(z), 0, 1)) * 2
  return(test)
  print(p)
}
regcount <- function(cname, elec){
  indices = colnames(mdb_junk)[which(filter(mdb_junk, Nation==cname, Election==elec)==1)]
  return(indices)
}  
```

###By-Nation Regression

```{r, echo=T}
unionval_table <- mdb_junk
unionval_table <- merge(unionval_table, natfac, by=c("Nation", "Election"))
nlist <- unionval_table$Nation
unionval_table$Population2 <- unionval_table$Population
for(i in 1:length(unionval_table$Population2)){
  unionval_table$Population2[i] <- unionval_table$Population2[i] / sum(nlist==unionval_table$Nation[i])
}

## Weighted
summary(lm(union_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table, weights=unionval_table$Population2))
summary(lm(pub_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table, weights=unionval_table$Population2))
summary(lm(urb_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table, weights=unionval_table$Population2))
summary(lm(IncomeAvg~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table, weights=unionval_table$Population2))
summary(lm(euro_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table, weights=unionval_table$Population2))

## Robustness check
summary(lm(union_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table))
summary(lm(pub_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table))
summary(lm(urb_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table))
summary(lm(IncomeAvg~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table))
summary(lm(euro_prem~BigRPFR+EUPos+EnviPos+LaborPos+WelfPos+ImmigPos+MCPPos+Comm,data=unionval_table))
```


### Plot of party categories by nation

```{r, echo=T}
merged_db_1 <- filter(merged_db, Nation != "Azerbaijan")

### All-in-one plot
plot1 <- ggplot(data=merged_db_1, 
              aes(fill=PSec, x=Nation))+
          geom_bar(position="fill",stat="count")+
          scale_fill_manual(labels = c("Social Democratic", "Center Right",
                                       "Liberal/Green", "Far Right",
                                       "Other/NI", "Communist"),
            values=c("red1","dodgerblue", "yellow", 
            "darkblue", "ivory4","red4")) +
          labs(x="Nation", y="Vote Share",
               fill="Party Category") +
          ggtitle("Party Category Vote Shares by Nation") +
          theme_bw() + scale_x_discrete(guide=guide_axis(n.dodge=2))
        

ggsave("party_cat_plot.png", plot1, width=15, height=7)


### Separate plots
aaa <- str_sort(unique(merged_db_1$Nation))
for(i in 1:3){
  merged_db_2 <- filter(merged_db_1, Nation %in% aaa[((13*i)-12):(13*i)])
  print(ggplot(data=merged_db_2, 
               aes(fill=PSec, x=Nation))+
          geom_bar(position="fill",stat="count")+
          scale_fill_manual(labels = c("Social Democratic", "Center Right",
                                       "Liberal/Green", "Far Right",
                                       "Other/NI", "Communist"),
            values=c("red1","dodgerblue", "yellow", 
            "darkblue", "ivory4","red4")) +
          labs(x="Nation", y="Vote Share",
               fill="Party Category") +
          ggtitle("Party Category Vote Shares by Nation") +
          theme_bw() + scale_x_discrete(guide=guide_axis(n.dodge=2))
        )
}
```

### Overall regression specification

```{r, echo=T}
table(merged_db_1$PSec)/length(merged_db_1$PSec)
merged_db_3 <- filter(merged_db_1, PSec %in% c("Left", "CenR", "CLib.G", "FarR"))
table(merged_db_3$PSec)/length(merged_db_3$PSec)
merged_db_3$PSec <- as.factor(as.character(merged_db_3$PSec))
test <- multinom(PSec~Union+Gender+PubWork+Edu+Empl+MarStat+Urban+Income+EuroTrust+Age+Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db_3, weights = merged_db_3$popweight, maxit=200)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
print(test)
print(p)
```

### Interaction specification

```{r, echo=T}
merged_db_1$EmplFac <- as.factor(merged_db_1$Empl)
merged_db_1$EduFac <- as.factor(as.numeric(as.numeric(merged_db_1$Edu) >= 6))
merged_db_1$AgeFac <- as.factor(2 - (merged_db_1$Age < 25) + (merged_db_1$Age > 54))
merged_db_1$GenderFac <- as.factor(as.numeric(merged_db_1$Gender == 0))

#Vars labeled Empl/Edu/Age/Gender : Empl UE, Edu BN, Age BPA, Gender MN, UNBN omitted
merged_db_1$UNBM <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 1 & merged_db_1$GenderFac == 1)
merged_db_1$UNPM <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 1)
merged_db_1$UNPN <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 0)
merged_db_1$UNAM <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 1)
merged_db_1$UNAN <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 0)
merged_db_1$UBBM <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 1 & merged_db_1$GenderFac == 1)
merged_db_1$UBBN <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 1 & merged_db_1$GenderFac == 0)
merged_db_1$UBPM <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 1)
merged_db_1$UBPN <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 0)
merged_db_1$UBAM <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 1)
merged_db_1$UBAN <- as.numeric(merged_db_1$EmplFac == 0 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 0)
merged_db_1$ENBM <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 1 & merged_db_1$GenderFac == 1)
merged_db_1$ENBN <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 1 & merged_db_1$GenderFac == 0)
merged_db_1$ENPM <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 1)
merged_db_1$ENPN <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 0)
merged_db_1$ENAM <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 1)
merged_db_1$ENAN <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 0 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 0)
merged_db_1$EBBM <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 1 & merged_db_1$GenderFac == 1)
merged_db_1$EBBN <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 1 & merged_db_1$GenderFac == 0)
merged_db_1$EBPM <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 1)
merged_db_1$EBPN <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 2 & merged_db_1$GenderFac == 0)
merged_db_1$EBAM <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 1)
merged_db_1$EBAN <- as.numeric(merged_db_1$EmplFac == 1 & merged_db_1$EduFac == 1 & merged_db_1$AgeFac == 3 & merged_db_1$GenderFac == 0)
merged_db_3 <- filter(merged_db_1, PSec %in% c("Left", "CenR", "CLib.G", "FarR"))
merged_db_3$PSec <- as.factor(as.character(merged_db_3$PSec))




test <- multinom(PSec~Union+PubWork+Urban+Income+EuroTrust+MarStat+
                   UNBM+UNPM+UNPN+UNAM+UNAN+UBBM+UBBN+UBPM+UBPN+UBAM+UBAN+ENBM+
                   ENBN+ENPM+ENPN+ENAM+ENAN+EBBM+EBBN+EBPM+EBPN+EBAM+EBAN+
                   Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db_3, weights = merged_db_3$popweight, maxit=200)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
print(test)
print(p)
```

### Equal weighting robustness check

```{r, echo=T}
merged_db_3 <- filter(merged_db_1, PSec %in% c("Left", "CenR", "CLib.G", "FarR"))
merged_db_3$PSec <- as.factor(as.character(merged_db_3$PSec))
test <- multinom(PSec~Union+Gender+PubWork+Edu+Empl+MarStat+Urban+Income+EuroTrust+Age+Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db_3, weights = merged_db_3$eqweight, maxit=200)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
print(test)
print(p)
```


### Coverage Analysis: EES. EVS, ESS Factors
```{r, echo=T}
#Gender
(nrow(evsnat)-sum(is.na(evsnat$Gender)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$Gender)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$Gender)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$Gender)))/nrow(merged_db)
#Age
(nrow(evsnat)-sum(is.na(evsnat$Age)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$Age)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$Age)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$Age)))/nrow(merged_db)
#Income
(nrow(evsnat)-sum(is.na(evsnat$Income)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$Income)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$Income)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$Income)))/nrow(merged_db)
#MarStat
(nrow(evsnat)-sum(is.na(evsnat$MarStat)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$MarStat)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$MarStat)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$MarStat)))/nrow(merged_db)
#PubWork
(nrow(evsnat)-sum(is.na(evsnat$PubWork)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$PubWork)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$PubWork)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$PubWork)))/nrow(merged_db)
#EuroTrust
(nrow(evsnat)-sum(is.na(evsnat$EuroTrust)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$EuroTrust)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$EuroTrust)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$EuroTrust)))/nrow(merged_db)
#Urban
(nrow(evsnat)-sum(is.na(evsnat$Urban)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$Urban)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$Urban)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$Urban)))/nrow(merged_db)
#Edu
(nrow(evsnat)-sum(is.na(evsnat$Edu)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$Edu)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$Edu)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$Edu)))/nrow(merged_db)
#Empl
(nrow(evsnat)-sum(is.na(evsnat$Empl)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$Empl)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$Empl)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$Empl)))/nrow(merged_db)
#Union
(nrow(evsnat)-sum(is.na(evsnat$Union)))/nrow(evsnat)
(nrow(essnat)-sum(is.na(essnat$Union)))/nrow(essnat)
(nrow(eesnat)-sum(is.na(eesnat$Union)))/nrow(eesnat)
(nrow(merged_db)-sum(is.na(merged_db$Union)))/nrow(merged_db)
```

### Descriptive statistics

```{R, echo=T}
mdb_1 <- merged_db
mdb_1$Edu <- as.numeric(mdb_1$Edu)
mdb_1$Gender <- as.numeric(mdb_1$Gender)
mdb_1$Gender[mdb_1$Gender==2] <- 0

mdb_2 <- mdb_1 %>% 
  group_by(Nation) %>% 
  summarise(Union=mean(Union, na.rm=T),Age=mean(Age, na.rm=T),
            PubWork=mean(PubWork, na.rm=T),Income=mean(Income, na.rm=T),
            Empl=mean(Empl, na.rm=T),Edu=mean(Edu, na.rm=T),
            Gender=mean(Gender, na.rm=T), Urban=mean(Urban, na.rm=T),
            MarStat=mean(MarStat, na.rm=T), EuroTrust=mean(EuroTrust, na.rm=T))
#Overall means
mean(mdb_1$Gender, na.rm=T)
mean(mdb_1$Age, na.rm=T)
mean(mdb_1$Income, na.rm=T)
mean(mdb_1$MarStat, na.rm=T)
mean(mdb_1$PubWork, na.rm=T)
mean(mdb_1$EuroTrust, na.rm=T)
mean(mdb_1$Urban, na.rm=T)
mean(mdb_1$Edu, na.rm=T)
mean(mdb_1$Empl, na.rm=T)
mean(mdb_1$Union, na.rm=T)
#Mean of national means
mean(mdb_2$Gender, na.rm=T)
mean(mdb_2$Age, na.rm=T)
mean(mdb_2$Income, na.rm=T)
mean(mdb_2$MarStat, na.rm=T)
mean(mdb_2$PubWork, na.rm=T)
mean(mdb_2$EuroTrust, na.rm=T)
mean(mdb_2$Urban, na.rm=T)
mean(mdb_2$Edu, na.rm=T)
mean(mdb_2$Empl, na.rm=T)
mean(mdb_2$Union, na.rm=T)
#SD of national means
sd(mdb_2$Gender, na.rm=T)
sd(mdb_2$Age, na.rm=T)
sd(mdb_2$Income, na.rm=T)
sd(mdb_2$MarStat, na.rm=T)
sd(mdb_2$PubWork, na.rm=T)
sd(mdb_2$EuroTrust, na.rm=T)
sd(mdb_2$Urban, na.rm=T)
sd(mdb_2$Edu, na.rm=T)
sd(mdb_2$Empl, na.rm=T)
sd(mdb_2$Union, na.rm=T)
```


### Robustness checks
```{r, echo=T}
merged_db_3 <- filter(merged_db_1, PSec %in% c("Left", "CenR", "CLib.G", "FarR") 
                      & datadummy==4)
table(merged_db_3$PSec)/length(merged_db_3$PSec)
merged_db_3$PSec <- as.factor(as.character(merged_db_3$PSec))
test <- multinom(PSec~Union+Gender+PubWork+Edu+Empl+MarStat+Urban+Income+EuroTrust+Age+Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db_3, weights = merged_db_3$popweight, maxit=200)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
print(test)
print(p)

merged_db_3 <- filter(merged_db_1, PSec %in% c("Left", "CenR", "CLib.G", "FarR") 
                      & datadummy==3)
table(merged_db_3$PSec)/length(merged_db_3$PSec)
merged_db_3$PSec <- as.factor(as.character(merged_db_3$PSec))
test <- multinom(PSec~Union+Gender+PubWork+Edu+Empl+MarStat+Urban+Income+EuroTrust+Age+Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db_3, weights = merged_db_3$popweight, maxit=200)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
print(test)
print(p)

merged_db_3 <- filter(merged_db_1, PSec %in% c("Left", "CenR", "CLib.G", "FarR") 
                      & datadummy %in% c(1,2))
table(merged_db_3$PSec)/length(merged_db_3$PSec)
merged_db_3$PSec <- as.factor(as.character(merged_db_3$PSec))
test <- multinom(PSec~Union+Gender+PubWork+Edu+Empl+MarStat+Urban+Income+EuroTrust+Age+Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db_3, weights = merged_db_3$popweight, maxit=200)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
print(test)
print(p)

merged_db_3 <- filter(merged_db_1, PSec %in% c("Left", "CenR", "CLib.G", "FarR"))
table(merged_db_3$PSec)/length(merged_db_3$PSec)
merged_db_3$PSec <- as.factor(as.character(merged_db_3$PSec))
test <- multinom(PSec~Union+Gender+PubWork+Edu+Empl+MarStat+Urban+Income+EuroTrust+Age+Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db_3, weights = merged_db_3$eqweight, maxit=200)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
print(test)
print(p)
```


###Logit robustness check

```{r, echo=T}
summary(glm(Left~Union+Gender+PubWork+Edu+Empl+MarStat+Urban+Income+EuroTrust+Age+Gallagher_Prev_LSq+Gallagher_ENEP+Nation, data=merged_db, weights = merged_db$popweight))
```










